FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-11 paper.tex
Finish sentence

\Fp{} is essentially scientific notation---\fp{} numbers are represented by packing a sign bit, an exponent, and an fraction part (also called the ``significand'' or ``mantissa'') into contiguous bit fields.
The advantages of this representation are that allows for compact representation of both very small and very large numbers in a narrow range of bits---a 64-bit float can represent numbers as big as $2^{1024}$ and as small as $2^{-1074}$.
This range is sufficient to represent both Planck's constant as well as Avogadro's constant with reasonable accuracy, making 
The flip side is that not every real number within that wide range is representable as a \fp{} value---there is almost always some gap between the real number that we wish to represent and the \fp{} number that can represent.
Whenever a value we have doesn't have a precise representation, we must \emph{round} that real value to the nearest \fp{} value.
We call this gap error, and error, along with the finite nature of \fp{} values, means that we can run into some funny situations.

>>>>

\Fp{} is essentially scientific notation---\fp{} numbers are represented by packing a sign bit, an exponent, and an fraction part (also called the ``significand'' or ``mantissa'') into contiguous bit fields.
The advantages of this representation are that allows for compact representation of both very small and very large numbers in a narrow range of bits---a 64-bit float can represent numbers as big as $2^{1024}$ and as small as $2^{-1074}$.

This range is sufficient to represent both Planck's constant as well as Avogadro's constant with reasonable accuracy, making IEEE 754 \fp{} adequate for a wide range of numerical computations.
The flip side is that not every real number within that wide range is representable as a \fp{} value---there is almost always some gap between the real number that we wish to represent and the \fp{} number that can represent.
Whenever a value we have doesn't have a precise representation, we must \emph{round} that real value to the nearest \fp{} value.
We call this gap error, and error, along with the finite nature of \fp{} values, means that we can run into some funny situations.
